Models of Lambek calculus enriched with subexponentials

### 2019-03-15 PaperDraft.tex
representation theorem

\begin{theorem}
  Every unital quantale $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ with quantic conucleus $\Box$ is
  isomorphic to some relation quantale $\hat{\Box}$
\end{theorem}

\begin{proof}
  Consider a relational quantale by Brown and Gurr $\hat{\mathcal{Q}} = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ where:
  \begin{enumerate}
    \item $\hat{a} = \{ \langle b, c \rangle \: | \: b \cdot a \leq c \}$;
    \item $\widehat{a \cdot b} = \hat{a} \circ \hat{b}$;
    \item $\widehat{\bigvee a} = \bigvee \hat{a}$.
  \end{enumerate}

  Consider $\hat{\Box} \hat{a} = \bigvee $

  \begin{enumerate}
    \item $\hat{\Box} \hat{a} \subseteq \hat{a}$;
    \item $\hat{\Box} \hat{a} \subseteq \hat{\Box} \hat{\Box} \hat{a}$;
    \item $\hat{a} \subseteq \hat{b} \Rightarrow \hat{\Box}\hat{a} \subseteq \hat{\Box}\hat{b}$;
    \item $\hat{\Box}\hat{a} \circ \hat{\Box}\hat{b} \subseteq \Box(\hat{a} \circ \hat{b})$;
    \item $\hat{\Box}\hat{\varepsilon} = \hat{\varepsilon}$.
  \end{enumerate}

  Let us show that $\hat{\Box} \hat {a} = \widehat{\Box a} = \{ \langle b, c \rangle \: | \:  b \cdot \Box a \leq c \}$
\end{proof}

\begin{defin}
  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I \rangle$,
  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.

  A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
  $\mathcal{W}$ is a Kripke frame and $v : Tp \to 2^W$.

@@

  \begin{enumerate}
    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
    \item $\mathcal{M}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
  \end{enumerate}
\end{defin}

@@

\begin{defin}
  Mininal normal modal Lambek calculus is $L^{*}_{\bf 1} \land \lor$ with additional rule:

>>>>

Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and
$\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.

Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
\end{prop}

\begin{proof}
  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.

  Let $a \in S$, so $\bigvee a \in S$, but $f(a) \in f(\mathcal{S})$, so $f(\bigvee a) = \bigvee (f (a)) \in f(\mathcal{S})$,
  so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
\end{proof}

  Let $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ be a unital quantale and $\mathcal{S}$ is a subquantale of $\mathcal{Q}$.

  Then $\langle \mathcal{Q}, \Box_{\mathcal{S}} \rangle$ is isomorphic to some relational quantale of $A$
  wit some quantic conucleus $\hat{\Box}$.
\end{theorem}

\begin{proof}
  Consider a relational quantale proposed by Brown and Gurr. This quantale is 4-tuple $\theta(\mathcal{Q}) = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ defined as follows:
  \begin{enumerate}
    \item $\theta(a) = \{ \langle b, c \rangle \: | \: b \leq a \cdot c \}$;
    \item $\theta(a \cdot b) = \theta(a) \circ \theta(b)$;
    \item $\theta(\bigvee a) = \bigvee \theta(a)$;
    \item $\theta(\varepsilon) = \{ \langle b, c \rangle \: | \: b \cdot \varepsilon \leq c \} = \{ \langle b, c \rangle \: | \: b \leq c \}$
  \end{enumerate}

  Let $\mathcal{S} \subseteq \mathcal{Q}$, we define $\Box a = \{ s \: | \: s \in S, s \leq a \}$ is quantic conucleus.

  So, $\theta(S) \subseteq \theta(\mathcal{Q})$ is a subquantale of $\theta(\mathcal{Q})$.

  Let us define $\theta(\Box) \theta{a} := \bigvee \{ \theta{s} \: | \: \theta{s} \in \theta{S}, \theta{s} \subseteq \theta{a} \}$, so

  $\begin{array}{lll}
  &\theta(\Box a) = \{ \langle p, q \rangle \: | \: p \leq \Box a \cdot q \} = &\\
  &\{ \langle p, q \rangle \: | \: p \leq \bigvee \{ s \: | \: s \in S, s \leq a \} \cdot q \} = &\\
  &\theta(\bigvee_{s \in S, s \leq a} s) = & \\
  &\bigvee_{s \in S, s \leq a} \theta(s) = & \\
  &\bigvee \{ \theta(s) \: | \: s \in S, s \leq a \} = & \\
  &\bigvee \{ \theta(s) \: | \: \theta(s) \in \theta(S), \theta(s) \subseteq \theta(a) \} = \theta(\Box) \theta(a)& \\
  \end{array}$

\begin{theorem}
  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
\end{theorem}

\begin{defin}
  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I\rangle$,
  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$ with additional requirements:

\begin{enumerate}
    \item $R^2 a (b c) d \Leftrightarrow R^2 (a b) c d$;
    \item $I(b) \Leftrightarrow R a b a \& R b a a$;
    \item $a \leq b \Leftrightarrow I(c) \& R c a b$;
    \item $ $
\end{enumerate}
\end{defin}

\begin{defin}
  A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
  $\mathcal{W}$ is a Kripke frame and $v : Tp \to 2^W$.

@@

  \begin{enumerate}
    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R u v w \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R u w v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R w u v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \exists u, v \in W, S w u v \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
    \item $\mathcal{M}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
  \end{enumerate}
\end{defin}

@@

\begin{defin}
  Mininal normal modal Lambek calculus ($L{\bf K}$) is $L^{*}_{\bf 1} \land \lor$ with additional rule:
